sem

### 2022-12-07 scripts/workshop/sem.Rmd
wroking on lefchk tutorial

library(tidyverse)
library(magrittr)
library(piecewiseSEM)

@@

```{r}
dSep(sem)
summary(sem)
```

>>>>

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)

@@

```{r}
dSep(sem)
summary(sem)
```
Lefcheck example

```{r}
library(devtools) #Install from CRAN if you do not already have
install_github("jslefche/piecewiseSEM")
library(piecewiseSEM)
```

```{r}
shipley2009.modlist = list(
  lme(DD~lat, random = ~1|site/tree, na.action = na.omit, 
    data = Shipley),
  lme(Date~DD, random = ~1|site/tree, na.action = na.omit, 
    data = Shipley),
  lme(Growth~Date, random = ~1|site/tree, na.action = na.omit, 
    data = Shipley),
  glmer(Live~Growth+(1|site)+(1|tree), 
    family=binomial(link = "logit"), data = shipley2009) )
```

```{r}
sem.fit(shipley2009.modlist, shipley2009)
```
